Andres Karjus &nbsp;<font size='3'> evolutionary&nbsp;linguist | cultural&nbsp;data&nbsp;analytics&nbsp;scholar | digital&nbsp;humanities&nbsp;educator </font>

### 2022-10-05 index.Rmd
fix breaks

---
title: "Andres Karjus &nbsp;<font size='3'> evolutionary linguist | cultural data analytics scholar | digital humanities educator </font>"
output: 
  html_document: 
    theme: spacelab
    toc: no
    toc_depth: 4  
    toc_float:
      collapsed: no
---

>>>>

---
title: "Andres Karjus &nbsp;<font size='3'> evolutionary&nbsp;linguist | cultural&nbsp;data&nbsp;analytics&nbsp;scholar | digital&nbsp;humanities&nbsp;educator </font>"
output: 
  html_document: 
    theme: spacelab
    toc: no
    toc_depth: 4  
    toc_float:
      collapsed: no
---
